Why robot programming is hard

### 2014-09-04 paper.tex
Work work work

>>>>

Work on robot programming by demonstration (e.g., Cakmak {\sl et al}~\cite{cakmak-rss10}) reduces the need to interact with 3D visualizations by having users directly manipulate the robot. Nevertheless, participants in their user study found the 3D environment difficult to navigate TBD!!!

!!! Talk about Maya's work here on PBD with interactive Action Visualizations
http://www.roboticsproceedings.org/rss10/p48.pdf
